Blum axioms and nondeterministic computation of functions

### 2016-04-20 paper.tex
paper.tex: Simplify the introduction to "Quality Standards" even more.

Since we are trying to make a definition of non-deterministic computation of functions,
this definition must encompass both
the ``computation'' part and the ``non-deterministic'' part.

In the ``computation'' part,
we want not to fall in the realm of undecidable problems,
but neither we want to ``forget'' of some computable function.
Therefore,
the new definition must be \emph{computationally equivalent}
to the deterministic machines.

In the ``non-deterministic'' part,
we want to preserve the fact that
converting to deterministic machines seems
\footnote{
    Simulating nondeterminism under a polynomial slowdown would show that $\P = \NP$;
    showing that the slowdown must be exponential would show that $\P \neq \NP$.
    Although most researchers expect the later to be the case~\cite[p.~54]{Gasarch2012},
    as Papadimitriou noted~\cite[p.~412]{Papadimitriou1994},
    in the absence of a proof that $\P \neq \NP$
    we should not be too emphatic in stating the simulation \emph{require}
    (as opposed to \emph{seemingly require}) exponential slowdown.
}
to require an exponential slowdown.
Therefore,
our definition must exhibit this apparent exponential speedup
when computing, for instance, the characteristic function\footnotemark{} of $\SAT$.
\footnotetext{
    The characteristic function of a set $A$
    is the function $1_A$ defined by
    \begin{equation*}
        1_A(x) = \begin{cases}
            1, & \text{if $x \in A$}. \\
            0, & \text{if $x \notin A$}.
        \end{cases}
    \end{equation*}
}
This is the ``non-deterministic'' part.

Sections \ref{sec:godel-numberings} and~\ref{sec:blum-axioms}
formalize our requirements for the ``computation'' part
and the ``non-deterministic'' part,
respectively.

>>>>

We are trying to make a definition of non-deterministic computation of functions.
We want our definition to be reasonable,
in the sense of not falling in the realm of undecidable problems,
nor ``forgetting'' some computable function;
and we want our definition to be efficient,
in the sense to preserve the apparent\footnote{
    It is apparent in the sense that,
    if proven would show $\P \neq \NP$,
    and if disproved (showing a polynomial slowdown is the best we can do)
    would show $\P = \NP$.
    Although most researchers expect the former to be the case~\cite[p.~54]{Gasarch2012},
    as Papadimitriou noted~\cite[p.~412]{Papadimitriou1994},
    in the absence of a proof that $\P \neq \NP$
    we should not be too emphatic in stating the simulation \emph{require}
    (as opposed to \emph{seemingly require}) exponential slowdown.
}
exponential speed-up when solving,
for instance, the Boolean satisfiability problem
--- that is, there should be an exponential speed-up
when computing the characteristic function\footnotemark{} of $\SAT$.
\footnotetext{
    The characteristic function of a set $A$
    is the function $1_A$ defined to be $1$ for $x \in A$
    and $0$ for $x \notin A$.
}

Sections \ref{sec:godel-numberings} and~\ref{sec:blum-axioms}
formalize these reasonableness and efficiency requirements,
respectively.
